Explain urban regional function

### 2018-11-23 paper.tex
introduction

%motivation
There is a strong incentive to develop explainable FRI system, which \emph{explains} the identification of functional regions. 
Explainable FRI is beneficial for both system designers and end users.
For system designers, providing explanations help them better diagnose the system and improve system performance. 
For end users, explanations not only facilitate interpretation of the clustering results, but also incubate a wide range of applications, including traffic flow predictions, personalized trajectory recommendation, urban planning and so on.

@@

%figure ??? real example or made-up example
As shown in Fig.\ref{explanation-example}, the city has been partitioned into several functional regions. For a specific region $r_1$ with label $I$, the system delivers textual and visual descriptions. Firstly label $l$ is most likely to relate to a mixture of activities ``'' and ``'', because from the analysis of mobility data, these two activities bring in $\%$ of the traffic flow to region $r_1$. Secondly, under activity ``", two urban features ``'' and ``" are most popular, with highly positive sentiments collected from online reviews. Finally region $r_1$'s most representative urban features are exactly ``" and ``", thus the system \textbf{explains} why $r_1$ is labeled as $l$.

%highlight
We highlight a key property of the proposed system: the power to integrate heterogenous data sources. On one hand, explanations essentially involve semantics. In our system, the semantics of labels are expressed through urban activities and urban features, which are extracted from online review data. On the other hand, the cluster labels are obtained in mobility data. To obtain more reasonable explanations that comply with the clustering algorithm, the semantics are blended with moving patterns discovered in mobility data. In building such a system, we face two challenges.

@@

%manual label costly supervision in sufficient
The first one of it is to extract the urban feature from comment data.
Urban feature is a set of characters with special geographical attributes, e.g., clothes, school, bars and so on.
Most of our content data are comments of shops with the shop address.The feature extracted from it is more related to shop feature than urban feature.
Therefore, existing sentiment extraction model ~\cite{Lu2011Label} can not be used directly in our models.%urban feature
In order to get the location information from these content data, all features are extracted as~\cite{Zhang2015Sentires}.
We select typical features with a high frequency and high information entropy from it.

%unsupervised

%how to embed mobility data
And the second challenge is how to explain the features.
If the extracted urban features used for explanations can not correspond to the labeled activity used to identify functional regions, the explanations will not have a strong explanation power for the identification, or even will not be generated.
To improve the explanation power of our framework, we extract related urban feature and find the corresponding sentiment score between activity and urban feature from contents.
With the probability that region units belong to which function generated by DMR, we can applied matrix factorization to find the relativity between region units and latent factor, i,e urban feature.
The urban feature with highest relativity make an explanation for why corresponding region units are identified as such function.

@@

\textbf{Contribution.}
Our paper has an outstanding result in following several aspect:
\begin{itemize}
  \item To the best of our knowledge,we are the first to give explanation to urban functional region identification , which could improve the trustiness and satisfaction of users and urban system designers.
  \item After identify different functions, We use the contents with sentiment to find the typical urban feature within a region and make explanation.
  \item The explanation is given by latent factor model. We appplied matrix factorization to get the correlation coefficients between single region units and its features.
\end{itemize}

>>>>

%motivation
There is a strong incentive to develop explainable FRI system, which \emph{explains} the identification of functional regions. 
Explainable FRI is beneficial for both system designers and end users.
For system designers, explanations help them better diagnose the system and improve system performance. 
For end users, explanations not only facilitate interpretation of the clustering results, but also incubate a wide range of applications, including traffic flow predictions, personalized trajectory recommendation, urban planning and so on.

@@

%figure ??? real example or made-up example
As shown in Fig.\ref{explanation-example}, the city has been partitioned into several functional regions. For a specific region $r_1$ with label $l$, the system delivers textual and visual descriptions. Firstly label $l$ is most likely to relate to a mixture of activities ``'' and ``'', because from the analysis of mobility data, these two activities bring in $\%$ of the traffic flow to region $r_1$. Secondly, under activity ``", two urban features ``'' and ``" are most popular, with highly positive sentiments collected from online reviews. Finally region $r_1$'s most representative urban features are exactly ``" and ``", thus the system explains why $r_1$ is labeled as $l$.

%highlight
We highlight a key property of the proposed explainable FRI system: \textbf{the power to integrate heterogenous data sources to offer semantic explanations for mobility patterns}. On one hand, explanations essentially involve semantics, which are not available in pure mobility data (i.e. taxicab pick-ups and drop-offs). In our system, the semantics of labels are expressed through urban activities and urban features, both of which are extracted from textual data (i.e. online review data). On the other hand, the identification of functional region is based on mobility patterns. To generate reasonable explanations, our system blends in the semantics extracted from textual data and moving patterns discovered in mobility data.

In building such a system, we face two challenges.

@@

%manual label costly supervision in sufficient
The first challenge is how to efficiently extract urban features from online review data.
A naive approach is to maintain a manually constructed lexicon of urban features.
However, the lexicon is expensive to construct and maintain.
An alternative approach is to classify textual phrases with the supervision of a labelled set.
Again, the supervision is costly to obtain.

%unsupervised
To address the first challenge, we adopt an unsupervised approach to extract urban features from online review data.
Furthermore, urban features are characterized with geographical attributes, existing product feature extraction methods such as~\cite{Lu2011Label} are not directly applicable.
We implement a layered computation.
We first adopt NLP techniques to select a candidate set of features.  
Then we filter urban features which are most representative in geographical texts.

%how to embed mobility data
The second challenge arises from the integration of textual and mobility data.
To fully explain the functional of a region, our goal is to simultaneously discover semantic associations (i.e. how the given region is associated to each urban activity and urban feature) and mobility patterns (i.e. how the current traffic flow of a given region is affected by previous traffic flow).
This is not a trivial task.
The mobility patterns can be highly diverse for each region and each timepoint.
For example, people tend to gather in school region in the day, while in residence regions produces maximal traffic flow at night.
Restraining a global form shared by all mobility patterns is problematic.

To address the second challenge, we adopt a latent factor model to embed the semantic associations to predict traffic flows, i.e. the traffic flow of a region is aggregated over all activities, where each activity specific traffic flow is predicted by people's preferences on multiple urban features and the region's association with the same set of urban features.
Furthermore, we incorporate a bias curve in the prediction formula to represent mobility patterns. 
The bias curve is free shaped so that the forms of mobility patterns are not restrained

@@

\textbf{Contribution} of this work is three-fold:
\begin{itemize}
  \item To the best of our knowledge,we are the first to give explanation to urban functional region identification , which could improve the trustiness and satisfaction of users and urban system designers.
  \item After identify different functions, We use the contents with sentiment to find the typical urban feature within a region and make explanation.
  \item The explanation is given by latent factor model. We appplied matrix factorization to get the correlation coefficients between single region units and its features.
\end{itemize}
